---
title: "collinearity_tests"
author: "Claire Meuter"
date: "2022-11-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(usdm)
library(corrplot)
library(tidyverse)
library(raster)
library(tmap)
library(here)
library(sf)
library(ResourceSelection)

#miaand claire's file path
gdrive_data <- "/Volumes/GoogleDrive/Shared drives/Black_Bear_Aware/gdrive_data"

```
#from Jason's code: 
##Correlation/collinearity#
#Quick way to test for collinearity between covariates#
#cor.matrix <- cor(data)
#cor.matrix
#corrplot(cor.matrix)
#cor.matrix <- cor(data, method = c("pearson"))
#cor.matrix
#corrplot(cor.matrix)
#if you want to examine VIFs, you need to build a model first (with all covariates)
#vif(model)

```{r}
model<- load(here("models", "fire_model_allyears.rds")) #you have to name the object "model or it will not read in right

# dem + aspect + TRI + popdens + lc + road_dens + road_dist + 
   # streams_dist + urban_dist + rec_dist + forest_dist + forest_dens + 
   # dist_fire_1yr + dist_fire_23yrs + dist_fire_45yrs

```


```{r}
#read in the data
fire_model_data <- read_csv(here(gdrive_data, "/AnalysisData/model_df_climate/11_28_2022/fire_model_data_allyears.csv"))

```
```{r}
data_model_matrix <- model.matrix(~0+., data=fire_model_data) 
cor_matrix <- cor(data_model_matrix)
corrplot(cor_matrix)

cor_matrix_2 <- cor(cor_matrix, method = c("pearson"))

corrplot(cor_matrix_2)
cor_matrix
cor_matrix_2


cor_matrix_subset <- subset(cor_matrix > 0.7)

cor_matrix2_subset <- subset(cor_matrix_2 > 0.7 )



```
#This is all the pairs that have correlation higher than .7 under pearson
#dem and TRI: 0.81727627  
#popdens and lcdev_med_int: 0.767137070
#popdens and road_dens:   0.745547883   
#lcopen_water and streams_dist: 0.747383087
#road_dist and urban_dist: 0.88769380
#road_dist and rec_dist: 0.77553891
#urban_dist and rec_dist: 0.80105074  
#forest_dist and forest_dens: 0.78528789
#forest_dist and dist_fire_1yr: 0.80420434
#forest_dist and dist_fire_23yr: 0.85424612
#forest_dist and dist_fire_45yr: 0.84254649
#dist_fire_1yr and dist_fire_23yr: 0.92636484      
#dist_fire_1yr and dist_fire_45yr: 0.92427803      
#dist_fire_23yr and dist_fire_45yr: 0.94269042
