---
title: "Remaining Data Wrangling"
author: "Mia Guarnieri, Claire Meuter"
date: '2022-10-18'
output: html_document
---

##Setup and packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#attach packages
#note - Loading all of the ones Jason used, I don't think we will need all of them 

library(tidyverse)
library(here)
library(terra)
library(sf)
library(tmap)

#mia and claire's file path
gdrive_data <- "/Volumes/GoogleDrive/Shared drives/Black_Bear_Aware/gdrive_data"

```

#Data Wrangling Prior to Coding

*Data Sources*: Please see ReadMe file for metadata and citations.
*Reference Paper*: Insert hagani citation here

#Load in necessary data layers

##California raster

Insert info about CA raster layer here

```{r}

ca_raster <- rast(here(gdrive_data, "/IntermediateData/IntermediateData_Files/CARaster_Tiger_Reclassed/CARaster_Tiger_Reclassed.img"))

#check the coordinate reference system 
crs(ca_raster)

#plot CA raster to confirm
tm_shape(ca_raster) +
  tm_raster() +
  tmap_mode("view")

```

##Conflict data

Insert info about WIR data here

```{r}
#Buffer conflict points to create conflict raster
```

##Elevation (DEM, mean elevation)

Two separate DEM rasters were available at 7.5-arc second resolution from USGS EROS. These will need to be merged together. Units of elevation are m.

```{r}

#northern California raster

dem_norcal <- rast(here(gdrive_data, "/InputData/InputData_Files/2010_DEM_USGSEROS_Norcal/30n150w_20101117_gmted_mea075.tif"))

#southern California raster

dem_socal <- rast(here(gdrive_data, "/InputData/InputData_Files/2010_DEM_USGSEROS_Socal/30n120w_20101117_gmted_mea075.tif"))

#merging the two rasters

dem_ca <- merge(dem_norcal, dem_socal)

#reproject to the same crs (NAD 83, CA Albers (2011))
dem_calbers <- project(dem_ca, ca_raster)

#cropping the files to the spatial extent of CA

dem_clipped <- mask(dem_calbers, ca_raster)

#plot DEM raster
tm_shape(dem_clipped) +
  tm_raster() +
  tmap_mode("view")

```

```{r}
#Save reclassified, reprojected, and clipped rasters to the data drive

#DO NOT RUN THIS MORE THAN ONCE

saverast <- function(x){
  
  name <- paste0(deparse(substitute(x)), ".tif") #the name of the file will be the same as the input object, plus '.tif' at the end
  
  #write the raster into the correct folder in drive (the path will need to be updated for other files) and save it as a geotiff
  
  writeRaster(x, filename = here(gdrive_data, "/IntermediateData/IntermediateData_Files/Elevation_Formatted", name), filetype = "GTiff")
  
}
```


##Road density

```{r}
road_density_2014 <- rast(here(gdrive_data,"/InputData/InputData_Files/2014_UsaRoadDensity_ESRI/2014_UsaRoadDensity_ESRI.tif"))
```


#Adjust the data to the same geographic extent and projection

##Elevation
```{r}
#reproject to the same crs (NAD 83, CA Albers (2011))
dem_calbers <- project(dem_ca, ca_raster)

#cropping to the spatial extent of CA
dem_mask <- mask(dem_calbers, ca_raster)

```

##Road density

```{r}

```

#Create remaining data layers

```{r}

```

##Aspect

```{r}

```

##Terrain ruggedness

```{r}

```

##Distance to road

```{r}
distance_to_roads <- distanceFromPoints(object = road_density_2014, xy=points)



```

##Distance to streams

```{r}

```

##Distance to urban areas

```{r}

```

##Distance to recreational areas

```{r}

```

##Distance to forest cover

```{r}


```

